Watch Out for the Bully! Study of Interference Between Jobs Running Concurrently on Dragonfly Network

### 2016-03-08 draft.tex
add some TODO and NOTE

@@

\section{Application Study}
\label{sec:app study}

% The amount of transferring data of each application are shown in Figure \ref{fig:3app-data-amount}.

@@

 Here will talk about network configuration, such as network scale, link bandwidth etc. \\

@@

@@

\begin{figure*}[t!]
    \centering
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{wkld/tl-traffic}
        \caption{Terminal Link Traffic}
        \label{fig:terminal-link-traffic}
    \end{subfigure}%
    \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{wkld/lc-traffic}
        \caption{Local Channel Traffic}
        \label{fig:local-channel-traffic}
    \end{subfigure}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{wkld/gc-traffic}
        \caption{Global Channel Traffic}
        \label{fig:global-channel-traffic}
    \end{subfigure}%
   \caption{Network Traffic.}
   \label{fig:wkld-network-traffic}
\end{figure*}

\begin{figure*}[t!]
    \centering
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{wkld/tl-stime}
        \caption{Terminal Link Busy Time}
        \label{fig:terminal-link-stime}
    \end{subfigure}%
    \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{wkld/lc-stime}
        \caption{Local Channel Busy Time}
        \label{fig:local-channel-stime}
    \end{subfigure}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{wkld/gc-stime}
        \caption{Global Channel Busy Time}
        \label{fig:global-channel-stime}
    \end{subfigure}%
   \caption{Network Channel Busy Time.}
   \label{fig:wkld-network-stime}
\end{figure*}

Figure \ref{fig:wkld-network-traffic} and Figure \ref{fig:wkld-network-stime} shows that random job placement with adaptive routing can distribute workload traffic and balance the load over the network. Contiguous job placement

@@

Figure \ref{fig:apps-commtime} shows the communication time of three applications running concurrently with 4 different placement and routing configurations. MG and CR can get improvement with random placement and adaptive routing, compared with contiguous placement and minimal routing. However, AMG's performance is impacted with random placement and adaptive routing, which makes it an exception from other applications.

@@

We look into network level to identify the major culprit behind AMG's abnormal behavior with random placement and adaptive routing. By identifying the terminal nodes and routers that each application's traffic go through, we can see that the traffic amount go through the routers that belongs to AMG is skyrocketing when it running with random placement and adaptive routing, shown in Figure \ref{fig:amg-lc-traffic} and Figure \ref{fig:amg-gc-traffic}. Adaptive routing will redirect the traffic of other applications to go through the routers belongs to AMG, and increase the burden of those routers, thus slow down the communication of AMG.

CrystalRouter and MultiGrid can get obvious benefit from random placement and adaptive routing, as we can see from Figure \ref{fig:cr-gc-traffic} \ref{fig:cr-lc-traffic} and Figure \ref{fig:mg-gc-traffic} \ref{fig:mg-lc-traffic}, random placement and adaptive routing can redirect their traffic to other region of network, to avoid local congestion as appeared with contiguous and minimal routing.

@@

@@

The communication time of each application shown in Figure \ref{fig:syn-apps-commtime}. The ``bully" become the ``bullyee". The less communication-intensive application, CrystalRouter and MultiGrid, suffer prolonged communication time when running concurrently with sAMG with random placement and adaptive routing configuration. The routers that belongs to MultiGrid  and now CrystalRouter has extra traffic go through them, shown in Figure  \ref{fig:syn-mg-lc-traffic} \ref{fig:syn-mg-gc-traffic} and Figure \ref{fig:syn-cr-lc-traffic} \ref{fig:syn-cr-gc-traffic}. The extra traffic come from sAMG, that been redirected by adaptive routing.

@@

>>>>

\newcommand{\TODO}[1]{\hl{TODO: #1}}
\newcommand{\NOTE}[1]{\hl{NOTE: #1}}
\newcommand{\changed}[1]{\textcolor{red}{#1}}

@@

@@

 \TODO{Here will talk about network configuration, such as network scale, link bandwidth etc. }\\

@@

\subsection{Application}
\label{sec:app study}

@@

\begin{figure*}[t!]
    \centering
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{wkld/tl-traffic}
        \caption{Terminal Link Traffic}
        \label{fig:terminal-link-traffic}
    \end{subfigure}%
    \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{wkld/lc-traffic}
        \caption{Local Channel Traffic}
        \label{fig:local-channel-traffic}
    \end{subfigure}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{wkld/gc-traffic}
        \caption{Global Channel Traffic}
        \label{fig:global-channel-traffic}
    \end{subfigure}%
   \caption{Network Traffic. \TODO{More explanation to be added for this figure}}
   \label{fig:wkld-network-traffic}
\end{figure*}

\begin{figure*}[t!]
    \centering
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{wkld/tl-stime}
        \caption{Terminal Link Busy Time}
        \label{fig:terminal-link-stime}
    \end{subfigure}%
    \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{wkld/lc-stime}
        \caption{Local Channel Busy Time}
        \label{fig:local-channel-stime}
    \end{subfigure}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{wkld/gc-stime}
        \caption{Global Channel Busy Time}
        \label{fig:global-channel-stime}
    \end{subfigure}%
   \caption{Network Channel Busy Time. \TODO{More explanation to be added for this figure}}
   \label{fig:wkld-network-stime}
\end{figure*}

Contiguous placement allocates each job a set of nodes that adjacent to each other, which confines the traffic of the application into the local area when coupled with minimal routing. This may leads to hot-spot in local area and unbalanced network utilization. As we can see from Figure \ref{fig:wkld-network-traffic} and \ref{fig:wkld-network-stime}, contiguous placement coupled with minimal routing always leads to the extreme high traffic amount for some routers , and thus longest network busytime.

Figure \ref{fig:wkld-network-traffic} and Figure \ref{fig:wkld-network-stime} shows that random job placement with adaptive routing can uniformly distribute workload traffic and balance the load over the network.

@@

Figure \ref{fig:apps-commtime} shows the communication time of three applications running concurrently with 4 different placement and routing configurations. MG and CR can get improvement with random placement and adaptive routing, compared with contiguous placement and minimal routing. However, AMG's performance is impacted with random placement and adaptive routing, which makes it an exception from other applications.  \TODO{More explanation about contiguous placement and minimal routing here}

@@

We look into network level to identify the major culprit behind AMG's abnormal behavior with random placement and adaptive routing. By identifying the terminal nodes and routers that each application's traffic go through, we can see that the traffic amount go through the routers that belongs to AMG is skyrocketing when it running with random placement and adaptive routing, shown in Figure \ref{fig:amg-lc-traffic} and Figure \ref{fig:amg-gc-traffic}. Adaptive routing will redirect the traffic of other applications to go through the routers belongs to AMG, and increase the burden of those routers, thus slow down the communication of AMG. \TODO{More explanation about contiguous placement and minimal routing}

CrystalRouter and MultiGrid can get obvious benefit from random placement and adaptive routing, as we can see from Figure \ref{fig:cr-gc-traffic} \ref{fig:cr-lc-traffic} and Figure \ref{fig:mg-gc-traffic} \ref{fig:mg-lc-traffic}, random placement and adaptive routing can redirect their traffic to other region of network, to avoid local congestion as appeared with contiguous and minimal routing. \TODO{More explanation about contiguous placement and minimal routing}

@@

We have tried three different congestion sensing schemes that used in adaptive routing\cite{dally-dragonfly}, although there are some variations of the experiments, none of the congestion sensing scheme can prevent the ``bully" from happening.

@@

The communication time of each application shown in Figure \ref{fig:syn-apps-commtime}. The ``bully" become the ``bullyee". The less communication-intensive application, CrystalRouter and MultiGrid, suffer prolonged communication time when running concurrently with sAMG with random placement and adaptive routing configuration. The routers that belongs to MultiGrid  and now CrystalRouter has extra traffic go through them, shown in Figure  \ref{fig:syn-mg-lc-traffic} \ref{fig:syn-mg-gc-traffic} and Figure \ref{fig:syn-cr-lc-traffic} \ref{fig:syn-cr-gc-traffic}. The extra traffic come from sAMG, that been redirected by adaptive routing. \TODO{More explanation about contiguous placement and minimal routing}.

@@

\NOTE{We can add another set of synthetic workload, in which three applications have similar data transfer amount, if necessary. }
